Assessing Lime

### 2019-08-27 README.Rmd
finished organizing journals

- Paper
    - Can you re-explain your vision with the minipage format?
- Internship
    - Dixon said he is fine with me switching to 10 hours in the spring (as long as Dr. Caragea agrees)
- Graphics Group
    - email list (should I be added as an admin?)
    - emailed Min (waiting for a response)
    - show updated schedule
    - Susan's idea (could we ask Joe, Erin, and/or Charlotte if they would be interested in preparing this talk?)

@@

- finish organizing journals and update contents in readme
- send out an email about graphics group plan for the first week
- finish reading new paper
- set up meeting with Danny on Friday once Heike sends me her availability
- add generalized R2 values to plots
- code up Laugel et al's work
- point out differences and similarities from the other paper (such as normal sampling)
- keep the LIME procedure at a higher level in the paper
- change to computing the $\mathcal{L}$ metric from the paper
- add figure descriptions in both caption and text
- go back through LIME procedure and update with new understanding (such as d' can be larger than d)
- add an assert_that statement in the code to check if the LIME package is changing
- read through papers giving an overview of the current explanation methods

@@

- `lime.png`: fun picture of a lime to use in the readme

@@

- `00-objectives_and_ideas`: background of the research project, goals of the project, concerns with LIME, and ideas to try
- `01-training_and_testing_data`: information on the Hamby data, understanding the raw data, and cleaning of the training and testing data
- `02-plotting_training_and_testing_data`: exploratory plots of the training and testing data
- `03-computation_issues`: documentation of some of the computation issues I ran into during the project
- `04-lime_algorithm_and_proposed_methods`: rough draft of the lime algorithm as implemented in the lime R package and proposed methods for improving the lime algorithm
- `05-applying_lime_to_rtrees`: application of lime and sensitivity analysis for many different input options
- `06-assessing_lime_explanations`: assessment of the lime explanations
- `07-logistic_regression`: logistic regressions fit to the bullet data and application of lime to the logistic regression
- `08-iris_comparison`: applying LIME to a random forest fit to the iris data
- `09-understanding_lime`: attempts to visualize the results from LIME to understand how LIME works
- `10-other_explainers`: trying out other model explainers

>>>>

- Paper
    - Can you re-explain your vision with the minipage format?
    - I cannot get LIME to work on my computer anymore...
- Internship
    - Dixon said he is fine with me switching to 10 hours in the spring (as long as Dr. Caragea agrees)
- Graphics Group
    - show updated schedule
    - email list (should I be added as an admin?)
    - Susan's idea (could we ask Joe, Erin, and/or Charlotte if they would be interested in preparing this talk?)
    - How to include an image in the preview of a post in blogdown?
    - Are you still available to talk next week?

@@

- finish reading new paper
- add generalized R2 values to plots
- code up Laugel et al's work
- point out differences and similarities from the other paper (such as normal sampling)
- keep the LIME procedure at a higher level in the paper
- change to computing the $\mathcal{L}$ metric from the paper
- add figure descriptions in both caption and text
- go back through LIME procedure and update with new understanding (such as d' can be larger than d)
- add an assert_that statement in the code to check if the LIME package is changing
- read through papers giving an overview of the current explanation methods

@@

- `lime.png`: fun picture of a lime to use in the readme
- `python-ridge1`, `python-ridge2`, and `python-ridge3`: screen shots of the python LIME package showing the use of a ridge regression as the explainer

@@

- `00-objectives_and_ideas`: background of the research project, goals of the project, concerns with LIME, and ideas to try
- `01-hamby_data_and_models`: information on the Hamby data, cleaning of the training and testing data, visualizations of the data, and models fit to the data (rtrees and logistic regressions)
- `02-understanding_lime`: explanation of LIME procedure
- `03-applying_lime`: applications of LIME to the models fit to the Hamby data
- `04-assessing_lime`: visual diagnostics for assessing the lime explanations
- `05-iris_comparison`: applying LIME to a random forest fit to the iris data
- `06-other_explainers`: trying out other model explainers
- `07-computation_issues`: documentation of some of the computation issues I ran into during the project

### 2019-08-27 journals/01-hamby_data_and_models/01-hamby_data_and_models.Rmd
finished organizing journals

---
title: "Hamby Data and `rtrees`"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: hide
---

@@

This journal includes a description of the Hamby datasets and the random forest model `rtrees` that will be used in this research project. Additionally, the specification and cleaning of the training and testing datasets are documented, and some initial visualizations of the random forest model are included.

```{r}
# Load libraries
library(bulletr)
library(cowplot)
library(plotly)
library(randomForest)
library(tidyverse)
```

@@

>>>>

---
title: "Hamby Data and `rtrees`"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

@@

This journal includes a description of the Hamby datasets and models fit to the data. The specification and cleaning of the training and testing datasets are documented, and some initial visualizations of the random forest model are included. The models included are the random forest model `rtrees` and several logistic regression models.

```{r}
# Load libraries
library(bulletr)
library(cowplot)
library(glmnet)
library(plotly)
library(randomForest)
library(tidyverse)
```

@@

# Logistic Regressions

I have been thinking a lot about it is difficult to determine whether LIME is providing reasonable explanations, because we cannot know what the random forest is doing. That is the point of LIME. Heike suggested that we fit a logistic regression model to the training bullet data. We can then apply LIME to the logistic regression and determine if the explanations match what we would expect based on the coefficients of the logistic regression that we can interpret. She also suggested including interactions in the logistic regression model. This section includes code for fitting several logisitic regression models.

### Main Effects Only

The code below fits a logistic regression model to the training data using the `train` function from the caret package. The nine features used to fit `rtrees` are included as main effects only. The features are standardized prior to fitting the model using the `preProcess = "scale"` in `train`.

```{r}
# Fit or load the logistic regression model with only main effects
if(!file.exists("../../../data/logistic_mains.rds")) {

  # Set a seed
  set.seed(20190226)

  # Fit the model
  logistic_mains <- caret::train(as.factor(samesource) ~ ccf + rough_cor + D + sd_D + 
                                   matches + mismatches + cms + non_cms + sum_peaks,
                                 preProcess = "scale",
                                 data = hamby173and252_train, 
                                 method = "glm", 
                                 family = "binomial")

  # Save the model
  saveRDS(logistic_mains, "../../../data/logistic_mains.rds")

} else{

  # Load the model
  logistic_mains <- readRDS("../../../data/logistic_mains.rds")

}
```

The output from the model is shown below. The features of ccf and matches stand out as the most important features in the model.

```{r}
# Summary of the model
summary(logistic_mains)
```

### All Two Way Interactions

The code below fits a logistic regression model to the training data using the `train` function from the caret package. The nine features used to fit `rtrees` are included as main effects and with all two way interactions. The features are standardized prior to fitting the model using the `preProcess = "scale"` in `train`.

```{r}
# Fit or load the logistic regression model with all two way interactions
if(!file.exists("../../../data/logistic_inters2.rds")) {

  # Set a seed
  set.seed(20190226)

  # Fit the model
  logistic_inters2 <- caret::train(as.factor(samesource) ~
                                       (ccf + rough_cor + D + sd_D + matches + 
                                          mismatches + cms + non_cms + sum_peaks)^2,
                                     preProcess = "scale",
                                     data = hamby173and252_train,
                                     method = "glm", 
                                     family = "binomial")

  # Save the model
  saveRDS(logistic_inters2, "../../../data/logistic_inters2.rds")

} else{

  # Load the model
  logistic_inters2 <- readRDS("../../../data/logistic_inters2.rds")

}
```

The output from this model is not shown.

```{r eval = FALSE}
# Summary of the model
summary(logistic_inters2)
```

### LASSO Model

```{r}
# Fit or load the lasso logistic regression model
if(!file.exists("../../../data/logistic_lasso.rds")) {

  # Set a seed
  set.seed(20190312)

  # LASSO logistic regression model
  logistic_lasso <- cv.glmnet(x = hamby173and252_train %>% select(rf_features) %>% as.matrix(ncol = 9), 
                              y = hamby173and252_train %>% pull(samesource) %>% as.numeric(),
                              alpha = 1,
                              family = "binomial")

  # Tell R to run the upcoming code in parallel
  # plan(multiprocess)

  # LASSO logistic regression model with possible pairwise interactions
  # logistic_lasso <- 
  #   hierNet.logistic.path(x = hamby173and252_train %>% select(rf_features) %>% as.matrix(ncol = 9), 
  #                         y = hamby173and252_train %>% pull(samesource) %>% as.numeric(), 
  #                         lamlist = logistic_lasso$lambda)

  # Save the model
  saveRDS(logistic_lasso, "../../../data/logistic_lasso.rds")

} else {

  # Load the model
  logistic_lasso <- readRDS("../../../data/logistic_lasso.rds")

}
```

### Comparing the Models

The results as computed by caret on the training data are shown below for the two logistic regression models. The accuracy shows that the models with two way interactions performs better on the training data.

```{r}
# Results from the models
data.frame(model = c("mains", "inters2")) %>%
  bind_cols(bind_rows(logistic_mains$results, logistic_inters2$results))
```

The AICs from the models are shown below. The model with two way interactions performs the best based on AIC.

```{r}
AIC(logistic_mains$finalModel)
AIC(logistic_inters2$finalModel)
```

I also wanted to know how the models perform on the test data. The models are used to make predictions on the test data and the MSEs are computed for each model. These are shown in the table below. The model with main effects only has the smallest MSE. I am guessing that the other model is overfitting the data.

```{r}
data.frame(obs = hamby224_test %>% 
             pull(samesource) %>% na.omit(),
           mains = predict(logistic_mains, hamby224_test %>% select(rf_features)),
           inters2 = predict(logistic_inters2, hamby224_test %>% select(rf_features))) %>%
  mutate(mains_sqerrs = (obs - as.logical(mains))^2,
         inters2_sqerrs = (obs - as.logical(inters2))^2) %>%
  summarise_at(vars(mains_sqerrs, inters2_sqerrs), 
               function(x) sum(x) / length(x)) %>%
  rename(mains_mse = mains_sqerrs, inters2_mse = inters2_sqerrs)
```

### 2019-08-27 journals/02-understanding_lime/02-understanding_lime.Rmd
finished organizing journals

---
title: "Understanding LIME"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: hide
---

>>>>

---
title: "Understanding LIME"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

### 2019-08-27 journals/03-applying_lime/03-applying_lime.Rmd
finished organizing journals

This journal includes a description of the random forest model `rtrees` fit to the bullet data by Eric and the code for applying lime to `rtrees`.

```{r}
# Load libraries
library(bulletr)
library(lime)
library(furrr)
library(future)
library(randomForest)
library(tidyverse)

@@

# Data

@@

# One Implementation

@@

# Multiple Implementations

@@

>>>>

This journal includes code for applying lime to various models (`rtrees` and logisitic regression with main effects only).

```{r}
# Load libraries
library(bulletr)
library(lime)
library(furrr)
library(future)
library(gretchenalbrecht)
library(randomForest)
library(tidyverse)

@@

@@

# Random Forest

### One Implementation

@@

### Multiple Implementations

@@

# Logistic Regression

```{r}
# Load the model
logistic_mains <- readRDS("../../../data/logistic_mains.rds")
```

### One Implementataion

The functions `lime` and `explain` from the lime package are applied below to the logisitc regression model with only main effects.

```{r}
# Create or load the lime and explain objects for the main effects logisitic regression model
if(!file.exists("../../../data/lime_explain_mains.rds")) {

  # Set a seed
  set.seed(20190226)

  # Apply lime
  lime_mains <- lime(x = hamby173and252_train %>%
                       select(rf_features), 
                     model = logistic_mains)

  # Apply explain
  explain_mains <- explain(x = hamby224_test %>%
                             select(rf_features) %>% 
                             na.omit(), 
                           explainer = lime_mains, 
                           n_labels = 1,
                           n_features = 3)

  # Join the lime and explain objects in a list
  lime_explain_mains <- list(lime = lime_mains, explain = explain_mains)

  # Save the lime and explain objects
  saveRDS(lime_explain_mains, "../../../data/lime_explain_mains.rds")

  # Load the lime and explain objects
  lime_explain_mains <- readRDS("../../../data/lime_explain_mains.rds")

### Multiple Implementations

The code below applies the LIME algorithm to the main effects logisitic regression model one time for the following different input cases:

```{r}
# Apply the run_lime function if the lime results file does not already exist
if(!file.exists("../../../data/logistic_lime_inputs.rds")) {

  # Specify the input options to use with lime
  logistic_lime_inputs <- list(bin_continuous = c(rep(TRUE, 20), 
                                                  rep(FALSE, 2)),
                               quantile_bins = c(rep(TRUE, 5), 
                                                 rep(FALSE, 5), 
                                                 rep(TRUE, 12)),
                               nbins = c(rep(2:6, 4), 
                                         rep(4, 2)),
                               use_density = c(rep(TRUE, 20), TRUE, FALSE),
                               bin_method = c(rep("quantile_bins", 5),
                                              rep("equally_spaced", 5),
                                              rep("tree", 10),
                                              rep("quantile_bins", 2)),
                               response = c(rep(NA, 10), 
                                            rep("samesource", 5), 
                                            rep("rfscore", 5), 
                                            rep(NA, 2)))

  # Apply lime to the full training data with the specified input options
  logistic_lime_explain <- future_pmap(.l = logistic_lime_inputs,
             .f = run_lime, # run_lime is one of my helper functions
             features = rf_features,
             train = hamby173and252_train,
             test = hamby224_test %>% 
               arrange(case) %>% 
               select(rf_features) %>% 
               na.omit(),
             rfmodel = logistic_mains,
             label = "TRUE",
             nfeatures = 3,
             seed = TRUE)

  # Separate the lime and explain function results from the full data
  logistic_lime <- map(logistic_lime_explain, function(list) list$lime)
  logistic_explain <- map_df(logistic_lime_explain, function(list) list$explain)

  # Name the items in the lime list
  names(logistic_lime) <- map_chr(1:22, function(case) 
      sprintf("case: bin_continuous = %s, quantile_bins = %s, nbins = %0.f, use_density = %s, bin_method = %s, response = %s",
              logistic_lime_inputs$bin_continuous[case],
              logistic_lime_inputs$quantile_bins[case],
              logistic_lime_inputs$nbins[case],
              logistic_lime_inputs$use_density[case],
              logistic_lime_inputs$bin_method[case],
              logistic_lime_inputs$response[case]))

  # Turn the lime input options into a dataframe before saving it
  logistic_lime_inputs <- logistic_lime_inputs %>%
    unlist() %>%
    matrix(ncol = length(logistic_lime_inputs), 
           dimnames = list(NULL, names(logistic_lime_inputs))) %>%
    as.data.frame() %>%
    mutate(case = 1:length(logistic_lime_inputs$quantile_bins)) %>%
    select(case, bin_continuous:response)

  # Save the lime objects
  saveRDS(logistic_lime_inputs, "../../../data/logistic_lime_inputs.rds")
  saveRDS(logistic_lime, "../../../data/logistic_lime.rds")
  saveRDS(logistic_explain, "../../../data/logistic_explain.rds")

  # Load in the lime objects
  logistic_lime_inputs <- readRDS("../../../data/logistic_lime_inputs.rds")
  logistic_lime <- readRDS("../../../data/logistic_lime.rds")
  logistic_explain <- readRDS("../../../data/logistic_explain.rds")

```{r}
# Create the test_explain combined data if the file does not already exist
if(!file.exists("../../../data/logistic_test_explain.rds")) {

  # Join the data and the explanations and edit and add additional variables
  logistic_test_explain <- hamby224_test %>%
    mutate(case = as.character(case)) %>%
    full_join(logistic_explain, by = "case") %>%
    mutate(case = factor(case),
           feature_desc = factor(feature_desc),
           feature = factor(feature),
           nbins = factor(nbins)) %>%
    arrange(nbins) %>%
    mutate(nbins = as.numeric(as.character(nbins)),
           situation = ifelse(bin_continuous == TRUE & bin_method == "quantile_bins", 
                              sprintf("%.0f quantile", nbins),
                              ifelse(bin_continuous == TRUE & bin_method == "equally_spaced",
                                     sprintf("%.0f equally spaced", nbins),
                                     ifelse(bin_continuous == TRUE & bin_method == "tree" &
                                              response == "samesource",
                                            sprintf("%.0f samesource tree", nbins),
                                            ifelse(bin_continuous == TRUE & bin_method == "tree" &
                                              response == "rfscore",
                                              sprintf("%.0f rfscore tree", nbins),
                                              ifelse(bin_continuous == FALSE & 
                                                     use_density == TRUE, 
                                                     "kernel density", 
                                                     "normal approximation"))))) %>%
             fct_relevel("2 quantile", "3 quantile", "4 quantile",
                         "5 quantile", "6 quantile", "2 equally spaced",
                         "3 equally spaced", "4 equally spaced",
                         "5 equally spaced", "6 equally spaced",
                         "2 samesource tree", "3 samesource tree",
                         "4 samesource tree", "5 samesource tree",
                         "6 samesource tree")) %>%
    mutate(bin_situation = ifelse(bin_method == "quantile_bins" & 
                                  bin_continuous == TRUE,
                                  "quantile",
                                  ifelse(bin_method == "equally_spaced" & 
                                         bin_continuous == TRUE,
                                         "equally spaced", 
                                         ifelse(bin_method == "tree" & 
                                                bin_continuous == TRUE & 
                                                response == "samesource",
                                                "samesource tree", 
                                                ifelse(bin_method == "tree" & 
                                                       bin_continuous == TRUE & 
                                                       response == "rfscore",
                                                       "rfscore tree", 
                                                       ifelse(bin_continuous == FALSE & 
                                                       use_density == TRUE, 
                                                       "kernel density", 
                                                       "normal approximation")))))) %>%
    mutate(bin_situation = factor(bin_situation))

  # Save the combined test and explain data
  saveRDS(logistic_test_explain, "../../../data/logistic_test_explain.rds")

  # Load in the data
  logistic_test_explain <- readRDS("../../../data/logistic_test_explain.rds")

```{r}
# Create the lime comparison data if the file does not already exist
if(!file.exists("../../../data/logistic_lime_comparisons.rds")) {

  # Create a data frame with the interesting information relating to the different
  # evaluations of lime and compute the difference and mean between the rf and rr
  # model predictions
  logistic_lime_comparisons <- logistic_test_explain %>%
    select(-data, -prediction) %>%
    group_by(case, bin_continuous, quantile_bins, nbins, use_density, bin_method, response) %>%
    slice(1) %>%
    ungroup() %>%
    select(situation, bin_situation, bin_method, bin_continuous, quantile_bins, response, 
           nbins, use_density, set, case, rf_features, rfscore, model_prediction, model_r2) %>%
    mutate(diff = rfscore - model_prediction,
           mean = (rfscore + model_prediction) / 2)

  # Save the lime comparison data frame
  saveRDS(logistic_lime_comparisons, "../../../data/logistic_lime_comparisons.rds")

  # Load in the lime comparison data frame
  logistic_lime_comparisons <- readRDS("../../../data/logistic_lime_comparisons.rds")

### 2019-08-27 journals/04-assessing_lime/04-assessing_lime.Rmd
finished organizing journals

---
title: "Assessing Lime"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
---

@@

```{r}
# Load libraries
library(gretchenalbrecht)
library(lime)
#library(seriation)
library(tidyverse)
library(randomForest)

# Load in the training data 
hamby173and252_train <- read.csv("../../../data/hamby173and252_train.csv")

# Load in the testing data (Hamby Data 224 Sets 1 and 11)
hamby224_test <- read.csv("../../../data/hamby224_test.csv") # created in the paper

# Read in the test_explain data
hamby224_test_explain <- readRDS("../../../data/hamby224_test_explain.rds")

hamby224_sensitivity_joined <- readRDS("../../../data/hamby224_sensitivity_joined.rds")

@@

# Visualization Ideas

@@

# One Implementation

## Accuracy

@@

### Complex versus Simple Model Predictions

@@

### Comparing Input Values by MSE and $R^2$

@@

## Consistency

@@

### Fleiss's Kappa

@@

### Tile Plots of Features Chosen

@@

### Attempts at Arranging the Tile Plots

@@

### Plot of Number of Features Chosen

@@

# Multiple Implementations

## Accuracy

@@

### Comparing MSE and $R^2$

@@

## Consistency

### Plots of Number of Features Chosen

@@

# Input Rankings

@@

# My LIME

### Random Forest Model

@@

### Visualizations of Data, Model, and LIME

@@

>>>>

---
title: "Assessing Lime"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

@@

```{r}
# Load libraries
library(gretchenalbrecht)
library(lime)
library(randomForest)
#library(seriation)
library(tidyverse)

# Load in the training and testing data 
hamby173and252_train <- read.csv("../../../data/hamby173and252_train.csv")
hamby224_test <- read.csv("../../../data/hamby224_test.csv")

# Read in the lime explanations
hamby224_test_explain <- readRDS("../../../data/hamby224_test_explain.rds")
hamby224_sensitivity_joined <- readRDS("../../../data/hamby224_sensitivity_joined.rds")

@@

# Random Forest

### Bar Charts of Bins

@@

### One Implementation

##### Accuracy

@@

**Complex versus Simple Model Predictions**

@@

**Comparing Input Values by MSE and $R^2$**

@@

##### Consistency

@@

**Fleiss's Kappa**

@@

**Tile Plots of Features Chosen**

@@

**Attempts at Arranging the Tile Plots**

@@

**Plot of Number of Features Chosen**

@@

### Multiple Implementations

##### Accuracy

@@

**Comparing MSE and $R^2$**

@@

##### Consistency

**Plots of Number of Features Chosen**

@@

### Rankings

@@

# Simpler Random Forest

### Model

@@

### Visualizations

@@

# Logistic Regression

```{r}
# Load the model
logistic_mains <- readRDS("../../../data/logistic_mains.rds")

# Read in the LIME explanations for the logistic regression
lime_explain_mains <- readRDS("../../../data/lime_explain_mains.rds")

# Read in the LIME comparisons for the logistic regression
logistic_lime_comparisons <- readRDS("../../../data/logistic_lime_comparisons.rds")

# Read in the combined test data and explanations
logistic_test_explain <- readRDS("../../../data/logistic_test_explain.rds")
```

### Visualizing Default LIME

```{r}
plot_features(lime_explain_mains$explain[1:12,])
```

```{r}
coefs <- logistic_mains$finalModel$coefficients %>% round(2)
```

The logistic regression model is

$\log\left(\frac{\hat{p}}{1-\hat{p}}\right)=$ `r coefs[[1]]` + `r coefs[[2]]` ccf + `r coefs[[3]]` rough_cor + `r coefs[[4]]` D + `r coefs[[5]]` sd_D + `r coefs[[6]]` matches + `r coefs[[7]]` mismatches + `r coefs[[8]]` cms + `r coefs[[9]]` non_cms + `r coefs[[10]]` sum_peaks

where $\hat{p}=P(\mbox{samesource = TRUE})$.

I started trying to compare the results from LIME to the logistic regression model, but I realized that I need to standardize my test data before I use the model to make predictions.

```{r}
m = function(x) coefs[2:10] * x
m(hamby224_test[1,] %>% select(rf_features))
hamby224_test[1:4,] %>% select(rf_features)
coefs
hamby224_test[1:4,] %>% select(rf_features) * coefs[2:10]
```

```{r}
mains_test_explain <- hamby224_test %>%
  mutate(case = as.character(case)) %>%
  full_join(lime_explain_mains$explain, by = "case") %>%
  mutate(case = factor(case),
         feature = factor(feature))
```

Below is a plot of the three chosen features for each of the cases faceted by set. The features are ordered by order they were chosen by lime (ordered by magnitude of the coefficients).

```{r}
mains_test_explain %>%
  na.omit() %>%
  arrange(case, desc(abs(feature_weight))) %>%
  mutate(feature_order = rep(c("first", "second", "third"), n() / 3)) %>%
  select(case, set, feature, feature_order) %>%
  spread(feature_order, feature) %>%
  arrange(set, first, second, third) %>%
  mutate(order = 1:n()) %>%
  gather(feature_order, feature, 3:5) %>%
  ggplot(aes(x = feature_order, y = order, fill = feature)) + 
  geom_tile() + 
  facet_grid(set ~ ., scales = "free_y") +
  theme_bw() +
  gretchenalbrecht::scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) + 
  labs(x = "Order of Features Chosen", y = "Case", fill = "Feature")
```

```{r}
pca_results <- princomp(hamby224_test %>% select(rf_features) %>% na.omit())
pca_results$loadings
z1 <- pca_results$scores[,1]
z2 <- pca_results$scores[,2]
ggplot(data.frame(z1, z2), aes(x = z1, y = z2)) + 
  geom_point()
biplot(pca_results)
```

### One Implementation

##### Accuracy

**Comparing Input Values by MSE and $R^2$**

```{r}
# Summarizing lime results
logistic_lime_results <- logistic_lime_comparisons %>%
  filter(!is.na(rfscore)) %>%
  group_by(situation, bin_situation, bin_continuous, quantile_bins, nbins, use_density, 
           bin_method, response, set) %>%
  summarise(mse = (sum(diff^2)) / length(diff),
            ave_r2 = mean(model_r2)) %>%
  arrange(set) %>%
  ungroup()
```

The plot below shows the mean squared errors for each of the input situations faceted by set. There is no one bin type that stands out as performing the best across all or most number of bins. This is unlike the results from the random forest model where the tree based bins usually performed the best.

```{r}
# Plot of MSEs
logistic_lime_results %>%
  mutate(bins = ifelse(nbins == 4 & bin_continuous == FALSE, "other", nbins)) %>%
  ggplot(aes(x = bin_situation, y = mse, color = bin_situation)) +
  geom_point() + 
  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
        legend.position = "none") + 
  labs(x = "Bin Type", y = "MSE", color = "") + 
  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
```

The plot below shows the average $R^2$ value for each of the input situations faceted by set. The results are very similar for each set, and the highest $R^2$ values occur for 2 quantile bins. With the logistic regression, the equally spaced bins or the quantile bins seem to perform the best in terms of $R^2$ across the different number of bins. The rfscore tree based bins are not as good as they were with the random forest model. However, all of the $R^2$ values are still very low for all cases.

```{r}
# Plot of R^2s
logistic_lime_results %>%
  mutate(bins = ifelse(nbins == 4 & bin_continuous == FALSE, "other", nbins)) %>%
  ggplot(aes(x = bin_situation, y = ave_r2, color = bin_situation)) +
  geom_point() + 
  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none") + 
  labs(x = "Bin Type", y = "Average R2", color = "") + 
  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
```

##### Consistency

```{r}
# Creates a dataset that creates columns of the chosen features by lime from first to third
logistic_chosen_features <- logistic_test_explain %>%
  filter(!(bin_situation %in% c("kernel density", "normal approximation"))) %>%
  filter(!is.na(rfscore)) %>%
  select(set, situation, bin_situation, nbins, case, samesource, feature, feature_weight) %>%
  mutate(feature_weight_abs = abs(feature_weight)) %>%
  arrange(situation, case, desc(feature_weight_abs)) %>%
  mutate(explainer = rep(c("first", "second", "third"), length(situation) / 3)) %>%
  select(-feature_weight, -feature_weight_abs) %>%
  spread(explainer, feature)
```

**Fleiss's Kappa**

I computed kappa for each bin situation separately for the top three features chosen. These values are plotted below for each set. For the first feature chosen by lime, the values of kappa suggest that quantile bins are the most consistent across all the number of bins followed by the samesource tree based bins.

```{r}
# Computes and plots the values of kappa
logistic_chosen_features %>%
  ungroup() %>%
  select(-situation) %>%
  gather(key = chosen, value = feature, first:third) %>%
  spread(nbins, feature) %>%
  select(-case) %>%
  rename(bins2 = "2", bins3 = "3", bins4 = "4", bins5 = "5", bins6 = "6") %>%
  group_by(set, bin_situation, chosen) %>%
  summarise(kappa = 
              irr::kappam.fleiss(matrix(c(bins2, bins3, bins4, bins5, bins6), 
                                        ncol = 5))$value) %>%
  arrange(chosen, set, bin_situation) %>%
  ggplot(aes(x = bin_situation, y = kappa, color = chosen, group = chosen)) +
  geom_point() + 
  geom_line() +
  facet_grid( ~ set) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  scale_color_gretchenalbrecht(palette = "pink_cloud", discrete = TRUE) +
  labs(x = "Bin Type", y = "Kappa", color = "Feature")
```

**Tile Plots of Features Chosen**

I also attempted to plot the features chosen by lime in order to visually assess the consistency. This plots are included below. The results appear to be different from the random forest results, but it is still possible to se vertical stripes that suggest a global interpretation as opposed to a local interpretation. However, the samesource bins do have some horizontal stipes that show what we would like to see. It is also interesting to note that the vertical bins are the most pronounced with the rfscore tree. This does not suprise me considering that these explanations are for a logistic regression and not the random forest model.

```{r fig.height = 8, fig.width = 8}
# Plots the top feature for each case for each bin situation
logistic_chosen_features %>%
  group_by(bin_situation, case) %>%
  mutate(nlevels = length(levels(factor(first)))) %>%
  ungroup() %>%
  arrange(bin_situation, set, samesource, desc(nlevels), case) %>%
  mutate(order = rep(rep(1:length(unique(case)), each = 5, 4))) %>%
  ggplot(aes(x = nbins, y = order, fill = first)) + 
  geom_tile() + 
  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
  theme_bw() + 
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) + 
  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
  labs(x = "Number of Bins", y = "Test Case", fill = "Feature", title = "First Feature")

# Plots the second feature for each case for each bin situation
logistic_chosen_features %>%
  group_by(bin_situation, case) %>%
  mutate(nlevels = length(levels(factor(second)))) %>%
  ungroup() %>%
  arrange(bin_situation, set, samesource, desc(nlevels), case) %>%
  mutate(order = rep(rep(1:length(unique(case)), each = 5, 4))) %>%
  ggplot(aes(x = nbins, y = order, fill = second)) + 
  geom_tile() + 
  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
  theme_bw() + 
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) + 
  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
  labs(x = "Number of Bins", y = "Test Case", fill = "Feature", title = "Second Feature")

# Plots the third feature for each case for each bin situation
logistic_chosen_features %>%
  group_by(bin_situation, case) %>%
  mutate(nlevels = length(levels(factor(third)))) %>%
  ungroup() %>%
  arrange(bin_situation, set, samesource, desc(nlevels), case) %>%
  mutate(order = rep(rep(1:length(unique(case)), each = 5, 4))) %>%
  ggplot(aes(x = nbins, y = order, fill = third)) + 
  geom_tile() + 
  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
  theme_bw() + 
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) + 
  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
  labs(x = "Number of Bins", y = "Test Case", fill = "Feature", title = "Third Feature")
```
